Liptschiz

### 2024-02-20 lipschitz/valabstraction.tex
update plots

\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
				set layers=default,
	xmax = 4, xmin = -4,
ymax = 1, ymin = -1,		
zmax = 1, zmin = -1,
				unit vector ratio=1 1 1, scale=1.5,
				view={60}{50}, ytick   = {-1,0,1},
				yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
				xticklabels = {$0$}, ztick   = {-1,0,1},
				zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

@@

\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
		set layers=default,
				xmax = 4, xmin = -4,
		ymax = 1, ymin = -1,		
				zmax = 1, zmin = -1,
		unit vector ratio=1 1 1, scale=1.5,  ytick   = {-1,0,1},
		yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
		xticklabels = {$0$}, ztick   = {-1,0,1},
		zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
		view={35}{14},
		]
		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

>>>>

The relation between $y_i$, $x_i$ and $\hat{y}_i$ is $$\hat{y}_i = \ReLU(x_i+y_i)-\ReLU(x_i).$$ And its plots is as follows:

\hspace*{-10ex}
\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
				set layers=default,
	xmax = 4, xmin = -4,
ymax = 1, ymin = -1,		
zmax = 1, zmin = -1,
				unit vector ratio=1 1 1, scale=3,
				view={60}{50}, ytick   = {-1,0,1},
				yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
				xticklabels = {$0$}, ztick   = {-1,0,1},
				zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

		\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(1,-1,-1)};
					\node[label={$(\gamma_i,-\gamma_i, -\gamma_i)$}] at (axis cs: 1.2, -0.5 ,-1) {};

			\addplot3[only marks, mark=*, mark size=2pt, blue] coordinates {(-1,1,0)};
		\node[label={$(-\gamma_i,\gamma_i, 0)$}] at (axis cs: -1, 0.8 ,0) {};

@@

\hspace*{-15ex}
\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
		set layers=default,
				xmax = 4, xmin = -4,
		ymax = 1, ymin = -1,		
				zmax = 1, zmin = -1,
		unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
		yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
		xticklabels = {$0$}, ztick   = {-1,0,1},
		zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
		view={35}{14},
		]
		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};
